SMT-Based Context-Bounded Model Checking for Embedded Systems (Position Paper)

### 2016-03-18 paper.tex
review induction-based verification

A feasible alternative to check properties in BMC is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. 
The simplest form of \textit{k}-induction consists of two steps: the \textit{base-case} and the \textit{induction-step}. In the former, the goal is to check whether $\phi$ holds in all states that are reachable from an initial state, within $k$ steps ($k \geq 0$ is assumed). The latter, in turn, aims to check that whenever $\phi$ holds, in $k$ consecutive states $s_1,\ldots,s_k$, $\phi$ also holds in the next system state $s_{k+1}$.

In particular, the \textit{k}-induction algorithm was successfully applied to ensure that (restricted) C programs do not contain violations related to data races~\cite{Donaldson10,Kinductor} and do respect time constraints, which were specified during the system design phase~\cite{EenS03}. Besides, \textit{k}-induction is a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,GrosseLD09,Sheera00}.

@@

\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software.}
\newblock {IEEE} Trans. Software Eng. \textbf{38}(4), pp. 957--974, 2012.

@@

>>>>

One possible way to achieve completeness in BMC techniques is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. However, the main limitation of such approach relies on producing or strengthening inductive assertions. In particular, loop invariants annotated in the program must be inductive (and not just invariant) for the corresponding VCs to be valid~\cite{Bradley07}. As a consequence, \textit{k}-induction procedures could even produce such assertions, which are indeed invariant, but if those assertions not inductive, then program correctness cannot be proved.

There are invariant generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory alignment in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature even report successful applications of induction-based verification for hardware and software systems, in some cases using invariants. In particular, \textit{k}-induction based verification was already applied to ensure that (restricted) C programs do not contain violations related to data races~\cite{Donaldson10,Kinductor} and do respect time constraints, which were specified during the system design phase~\cite{EenS03}. \textit{k}-induction is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,GrosseLD09,Sheera00}.

@@

\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}.
\newblock {IEEE} Trans. Software Eng. \textbf{38}(4), pp. 957--974, 2012.

\bibitem{Bradley07}
Bradley A., Manna Z.:
\newblock {\em The calculus of computation - decision procedures with applications to verification}. 
\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.

@@

\bibitem{pips:2013}
ParisTech M (2013) PIPS: Automatic Parallelizer and Code Transformation Framework. Accessed 21 February 2016

\bibitem{Henry:2012}
 Henry J, Monniaux D, Moy M (2012) PAGAI: A Path Sensitive Static Analyser. Electronic Notes in Theoretical Computer Science. Elsevier, pp. 15--25
